\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-03-31 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
changed & to and
updated the name of the absorbing condition flags in the manual

\item [{\texttt{ABSORBING\_CONDITIONS}}] Set to \texttt{.true.} to turn
on Clayton-Enquist absorbing boundary conditions (see \citet{KoTr99}).
\item [{\texttt{ABSORB\_INSTEAD\_OF\_FREE\_SURFACE}}] Set to \texttt{.true.} to turn on

@@

\item [{\texttt{PML\_WIDTH\_MIN}}] Gives a min. authorized bound to the solver to target an optimized thickness of C-PML layers.
\item [{\texttt{PML\_WIDTH\_MAX}}] Gives a max. authorized bound to the solver to target an optimized thickness of C-PML layers.

@@

\begin{itemize}
\item the simulation type control parameters: \texttt{SIMULATION\_TYPE}
and \texttt{SAVE\_FORWARD}
\item the time step parameters \texttt{NSTEP} and \texttt{DT}
\item the absorbing boundary control parameter \texttt{ABSORBING\_CONDITIONS} on condition that the\\
  \texttt{ABSORB\_INSTEAD\_OF\_FREE\_SURFACE} flag remains unmodified after running the databases generation.
\item the movie control parameters \texttt{MOVIE\_SURFACE}, \texttt{MOVIE\_VOLUME},
and \texttt{NTSTEPS\_BETWEEN\_FRAMES}
\item the ShakeMap\textregistered option \texttt{CREATE\_SHAKEMAP}
\item the output information parameters \texttt{MOVIE\_TYPE}, \texttt{NTSTEP\_BETWEEN\_OUTPUT\_INFO}
and \texttt{NTSTEP\_BETWEEN\_OUTPUT\_}~\\
\texttt{SEISMOS}
\item the \texttt{PRINT\_SOURCE\_TIME\_FUNCTION} flags
\end{itemize}
Any other change to the \texttt{Par\_file} implies rerunning both
the database generator \texttt{xgenerate\_databases} and the solver \texttt{xspecfem3D}.

@@

\chapter{\label{cha:Fault-Kinematics-Dynamics}Fault Kinematics \& Dynamics}

>>>>

\item [{\texttt{STACEY\_ABSORBING\_CONDITIONS}}] Set to \texttt{.true.} to turn
on Clayton-Enquist absorbing boundary conditions (see \citet{KoTr99}). In almost all cases it is much better to use CPML absorbing
layers (see the options below) and leave this flag to \texttt{.false.}.
\item [{\texttt{STACEY\_INSTEAD\_OF\_FREE\_SURFACE}}] Set to \texttt{.true.} to turn on

@@

@@

\begin{itemize}
\item the simulation type control parameters: \texttt{SIMULATION\_TYPE}
and \texttt{SAVE\_FORWARD}
\item the time step parameters \texttt{NSTEP} and \texttt{DT}
\item the absorbing boundary control parameter \texttt{PML\_CONDITIONS} on condition that the\\
  \texttt{PML\_INSTEAD\_OF\_FREE\_SURFACE} flag remains unmodified after running the databases generation.
\item the movie control parameters \texttt{MOVIE\_SURFACE}, \texttt{MOVIE\_VOLUME},
and \texttt{NTSTEPS\_BETWEEN\_FRAMES}
\item the ShakeMap\textregistered option \texttt{CREATE\_SHAKEMAP}
\item the output information parameters \texttt{MOVIE\_TYPE}, \texttt{NTSTEP\_BETWEEN\_OUTPUT\_INFO}
and \texttt{NTSTEP\_BETWEEN\_OUTPUT\_}~\\
\texttt{SEISMOS}
\item the \texttt{PRINT\_SOURCE\_TIME\_FUNCTION} flags
\end{itemize}
Any other change to the \texttt{Par\_file} implies rerunning both
the database generator \texttt{xgenerate\_databases} and the solver \texttt{xspecfem3D}.

@@

\chapter{\label{cha:Fault-Kinematics-Dynamics}Fault Kinematics and Dynamics}
